Binding of cations to phospholipid bilayers

### 2015-02-24 LIPIDionINTERACT/LIPIDionINTERACT.tex
update experimental data in lipid-ion interaction manuscript

\begin{figure}[]
  \centering
  \includegraphics[width=8cm]{OrderParameterIONSnaclSIGN.eps}
  \caption{\label{ordPnacl}
    Order parameters as a function of NaCl concentration from simulations 
     with the Berger, CHARMM36, MacRog and Orange force fields compared to the experiments
     by Akutsu et al.~\cite{akutsu81}. The signs are assumed to be the same as measured by Hong et al.~\cite{hong95a}, Hong et al.~\cite{hong95a} and Gross et al.~\cite{gross97}. 
     The effect of ions to the g2 and g3 were not measured, thus only the values without ions are shown. The straight line between the results with and without ions is 
     plotted to guide the eye. 
   }
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=8cm]{OrderParameterIONSnaclSIGN.eps}
  \caption{\label{ordPnacl}
    Order parameters as a function of NaCl concentration from simulations 
     with the Berger, CHARMM36, MacRog and Orange force fields compared to the experiments
     by Akutsu et al.~\cite{akutsu81} and Altenbach et al.~\cite{altenbach84}. The signs are assumed to be the same as measured by Hong et al.~\cite{hong95a}, Hong et al.~\cite{hong95a} and Gross et al.~\cite{gross97}. 
     The experimental data for the effect of ions to the glycerol backbone is not found, thus only the values without ions are shown. 
     The straight line between the results with and without ions is plotted to guide the eye. 
   }
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=8cm]{OrderParameterIONSCaCl.eps}
  \caption{\label{ordPcacl}
    Order parameters as a function of CaCl concentration from simulations 
     with the Berger 
%CHARMM36, MacRog 
and Orange force fields compared to the experiments by Akutsu et al.~\cite{akutsu81} and Altenbach et al.~\cite{altenbach84}. 
The signs are assumed to be the same as measured by Hong et al.~\cite{hong95a}, Hong et al.~\cite{hong95a} and Gross et al.~\cite{gross97}. 
     The effect of ions to the g1 and g2 were not measured, thus only the values without ions are shown. The straight line between the results with and without ions is 
     plotted to guide the eye. 
   }
\end{figure}
